\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-03-02 manuscript/paper.tex
update 3

  \node[rectangle, inner sep=8mm,draw=black!130, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.4cm, xshift=-8cm]{\Large$\bm{k = 1...K}$}}] at (6.5,0.4) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick, label={[anchor=west, yshift=-0.5cm, xshift=-2.7cm]{\Large$\bm{l = 1...L}$}}] {};

>>>>

  \node[rectangle, inner sep=8mm,draw=black!130, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.4cm, xshift=-8cm]{\Large$\bm{k = 1, \ldots,K}$}}] at (6.5,0.4) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick, label={[anchor=west, yshift=-0.5cm, xshift=-2.7cm]{\Large$\bm{l = 1, \ldots,L}$}}] {};
